%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Software \& Cloud Engineer (Innovation team){\enskip\cdotp\enskip}\it{Full-time}} % Job title
    {EVS Broadcast Equipment} % Organization
    {Liège, Belgium} % Location
    {Oct. 2022 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Involved in development, architecture and scalability aspects of a new cloud-based solution (Azure).}
      \end{cvitems}
    }

  \cventry
    {Software \& Cloud Software Engineer{\enskip\cdotp\enskip}\it{Full-time}} % Job title
    {} % Organization
    {} % Location
    {Jan. 2021 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Involved in development, architecture enhancement and scalability aspects of a cloud-based solution (AWS).}
        \item{Developed and improved containerized microservice applications and RESTful services using ASP.NET Core and .NET 5.0/6.0.}
        \item{Participated in the development, testing and deployment of web applications using React, Typescript and Cypress.}
        \item{Worked with container systems like Docker and container orchestration like Kubernetes or Amazon ECS/EKS, managed with Terraform.}
        \item{Used CI/CD pipelines automation (TeamCity) to drive all the builds out to the package or container registries.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer UX/UI{\enskip\cdotp\enskip}\it{Full-time}} % Job title
    {BT (previously IP Trade)} % Organization
    {Liège, Belgium} % Location
    {Sept. 2016 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % Develops, sells, manufactures, installs and supports, on a global scale, easy to integrate unified communication solutions for critical users
        % \item {Maintained and improved an easy to integrate Unified Communications solution for critical users.}
        \item{Participated in the development and improvement of an IP-based desktop telephony application (\colorhref[material-indigo]{http://www.iptrade-networks.com/products/turret/}{Turret}) written in C++/Qt/QML.}
        \item{Designed and implemented a RESTful HTTP/JSON backend server in C\# using ASP.NET Web API.}
        \item{Acquired strong analytical skills by solving multiple complex issues such as deadlocks in relational databases.}
        \item{Maintained and improved the Turret Support Server (TSS), a Microsoft ASP.NET web-based management and database application.}
        \item{Started to implement new VoIP Web Application from scratch with Angular.}
        \item{Collaborated with multiple teams daily to build full stack applications for dozens of clients.}
      \end{cvitems}
    }

  \cventry
    {Mobile Application Software Engineer{\enskip\cdotp\enskip}\it{End-of-studies Internship}} % Job title
    {Mobilu} % Organization
    {Bertrange, Luxembourg} % Location
    {Feb. 2016 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Learned about concepts in iOS app development, gained a deeper understanding of the Swift programming language.}
        \item{Evaluated and started developing a new iOS application from scratch with Swift.}
        \item{Modified existing Objective-C iOS applications and added new capabilities according users requirements.}
      \end{cvitems}
    }

  \cventry
    {Software Developer{\enskip\cdotp\enskip}\it{End-of-studies Internship}} % Job title
    {Haute école de la Province de Liège - EcoMotion Project} % Organization
    {Seraing, Belgium} % Location
    {Feb. 2013 - May 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created a desktop application (C++/Qt/SQLite/GSL) to interpret/analyze data extracted from an \colorhref[material-indigo]{https://team-ecomotion.com}{ultra-fuel-efficient racing car}.}
        \item{Participated in \colorhref[material-indigo]{https://www.shell.com/make-the-future/shell-ecomarathon.html}{Shell Eco-marathon}, one of the world's leading energy efficiency competitions.}
      \end{cvitems}
    }

\end{cventries}

%-------------------------------------------------------------------------------
%	TEMPLATE
%-------------------------------------------------------------------------------

%   \cventry
%     {} % Job title
%     {} % Organization
%     {} % Location
%     {} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item{}
%       \end{cvitems}
%       \begin{cvsubentries}
%         \cvsubentry{}{}{}{}
%         \cvsubentry{}{}{}{}
%       \end{cvsubentries}
%     }
